Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-05 ProbabilisticCoherence.tex
Cleaned up intro

Large collections of time series often follow some aggregation structure.  For example, the electricity demand of a country can be disaggregated according to a geographical hierarchy of states, cities, and individual households or according to temporal hierarchy of yearly, quarterly and monthly demand. In these so-called hierarchical time series, forecasts are often required for all individual series.  To ensure aligned decision making it is important for forecasts at the most disaggregated - or bottom-level - to add up to forecasts at more aggregated - or higher - levels. This property is referred to as ``coherence''.

Traditional approaches to ensure coherent point forecasts produce forecasts at a single level. For instance in the bottom-up \citep{Dunn1976} approach, forecasts are produced at the most disaggregated level and then summed to recover top level-series.  Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is produced and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast,while the middle-out approach is a hybrid between these two.

In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.  These methods produce first stage, or  so called `base' forecasts independently for each series.  Since base are rarely coherent in practice,  they are subsequently adjusted  or `reconciled' to ensure coherence.  To  date reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling least squares estimators. These include Ordinary Least Squares {OLS} \cite{Hyndman2011}, Weighted Least Squares {WLS} \todo{citation?} and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017}, more commonly referred to as MinT since it minimises the trace of  the squared error matrix. These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and in some sense hedge against the risk of model misspecification error in a single level.

A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \cite[see][and references therein]{Gneiting2014}.  Indeed to the best of our knowledge, the as yet unpublished work of \cite{BenTaieb2017} is the only paper to deal with the issue of coherent probabilistic forecasts, and although the means of the predictive distributions are reconciled, the overall distributions are constructed in a bottom up fashion.  In contrast, the main objective of our paper is to generalise point forecast reconciliation to probabilistic forecast reconciliation.

To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we  first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.  In addition to being highly intuitive, this allows us to establish a number of theoretical results.  We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts while the second shows that reconciled forecasts dominate unreconciled forecasts since projections are bounded operators.  We provide definitions of coherence and forecast reconciliation in the probabilistic setting and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.  We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.  We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly esitimated in practice, our  theoretical results lead to a heuristic argument in favour of MinT reconciliation.

We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules.  In particular we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.  As such we recommend the use of the energy score and variogram score for comparing reconciled to unreconciled forecasts.  Two or more reconciled forecasts can be compared using log score,energy score and  variogram score, although we show that comparisons should be  made on the full hierarchy for the latter two scores.

The remainder of the papers is  structured as follows.   In Section~\ref{sec:notation}, hierarchical time series are discussed in general and notation is  defined.  In section \ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.  Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.  In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian},  Section~\ref{sec:conclusions} concludes.

>>>>

Large collections of time series often follow some aggregation structure.  For example, the electricity demand of a country can be disaggregated according to a geographical hierarchy of states, cities, and individual households or by a temporal hierarchy of yearly, quarterly and monthly demand. In these so-called hierarchical time series, forecasts are often required for all individual series.  To ensure aligned decision making it is important for forecasts at the most disaggregated - or bottom-level - to add up to forecasts at more aggregated - or higher - levels. This property is referred to as ``coherence''.  This issue has been extensively covered for point forecasting in a literature we review below, while the case of probabilistic forecasting is a gap that we seek to address in this work.

Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level.  To describe these we use the small hierarchy in Figure~\ref{fig1}. In the bottom-up \citep{Dunn1976} approach, forecasts are produced at the most disaggregated level (Series {\em AA}, {\em AB}, {\em BA} and {\em BB}) and then summed to recover all top level-series.  Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is first produced (Series {\em Tot}) and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast. A middle-out approach is a hybrid between these two that for the hierarchy below would produce first stage forecasts for Series {\em A} and {\em B}.

In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.  For these methods, first stage forecasts are independently produced for all series rather than series at a single level.  Since these so-called `base' forecasts are rarely coherent in practice,  they are subsequently adjusted  or `reconciled' to ensure coherence.  To  date reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators. These include Ordinary Least Squares {OLS} \cite{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017} and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017}, more commonly referred to as MinT since it minimises the trace of  the squared error matrix. These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and in some sense hedge against the risk of model misspecification at a single level.

A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \cite[see][and references therein]{Gneiting2014}.  Indeed to the best of our knowledge, the as yet unpublished work of \cite{BenTaieb2017} is the only paper to deal with the issue of coherent probabilistic forecasts, and although the means of the predictive distributions are reconciled, the overall distributions are constructed in a bottom up fashion.  In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.

To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we  first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.  In addition to being highly intuitive, this allows us to establish a number of theoretical results.  We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts while the second shows that reconciled forecasts dominate unreconciled forecasts since projections are bounded operators.  We provide definitions of coherence and forecast reconciliation in the probabilistic setting and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.  We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.  We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.

We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules.  In particular we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.  As such we recommend the use of the energy score and variogram score for comparing reconciled to unreconciled forecasts.  Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be  made on the full hierarchy for the latter two scores.

The remainder of the papers is  structured as follows.   In Section~\ref{sec:notation}, hierarchical time series are discussed in general and notation is  defined.  In section \ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.  Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.  In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian} and Section~\ref{sec:conclusions} concludes.
